### 2024-02-15 documentation/thesis/thesis_document.tex
.

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field \gls{mri}research and
applications, articulates the research question driving this thesis and
delineates the anticipated usecases and benefits that will be explored
and analyzed throughout the study.

@@

In response to this, there is a growing interest in developing low-field
\gls{mri} systems that utilize in many cases permanent magnets. These
systems, while offering advantages in energy efficiency and reduced
complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While tipically calculated images have lower resolution due to
lower magnetic field strength, low-field systems facilitate the
comparison of different field behaviors and the identification of all
kinds of irritations. O'Reilly and Teeuwisse and de Gans
\cite{OReilly2019-rn} have already demonstrated low-cost and
small-scale implementations with low-field \gls{mri} in 2021
calculationg images of a head sucessfully.

@@

Completed \gls{mri} systems pose significant challenges for
retrospective adjustments, particularly when individual magnets impact
the overall homogeneity of the magnetic field. While deviations in
homogeneity can be measured post-assembly, the intricate task of
readjustment is taken into account. It is less costintensive and less
complicated to measure the magnets proactively, prior to the
finalization of the \gls{mri}system.

@@

For modern medical imaging high-field superconducting magnets dominate
most \gls{mri} machines, providing high blac-withe image resolution.
However, the substantial costs, space requierments and safety
considerations cause considerable challenges.

\gls{mri} relies on the presence of a robust magnetic field, and over
time, there has been a continual push to enhance the strength of these
magnetic fields. This strength is quantified in units of Tesla {[}T{]},
commonly referred to as the \emph{B0} field in medical contexts, while
physicists use the term magnetic field induction. The \gls{snr} is
proprtional to the magnetic \emph{B0} field; growing magnetic field
leads automatically to higher \gls{snr}. The inital \emph{B0} field of
an \gls{mri} aims to be homogenouse, for image aquisition the second
step requires imhomoginity of the \emph{B0} field to stimulate spin in
the atoms of materials. For high resultion images, the initial \emph{B0}
field aims to be a homogenouse as possible.

@@

A halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The graphic
\ref{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring, in which in this case eight
cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
magnetic flux densities of around \emph{20mT}.

@@

The Halbach magnetic array appears as a essential element for future
Magnet characterisation. Based on this fact this thesis centers on
assessing the sensors' applicability, the Halbach magnetic array serves
as a tool for later measurements, although its implementation and
further discussion will not be the primary focus.

@@

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
\cite{OReilly2019-rn} in 2019.This innovative setup was subsequently
employed in 2020 to acquire in vivo MR images, showcasing the practical
applications of their pioneering research \cite{OReilly2021-ep}.
2023 veröffentlichten de Vos, Remis und Webb eine zusammenfassung zur
gestaltng eines oint-of-care halbach array low-field \gls{mri} system
\cite{De_Vos2023-pb}.

Within the research domain, various implementations came up. An exemplar
instance is the work by O'Reilly, Teeuwisse, and Webb, who introduced a
groundbreaking ``three-dimensional \gls{mri} in a homogeneous 27cm
diameter Bore Halbach Array magnet'' \cite{OReilly2019-rn} in 2019.
This innovative setup was subsequently employed in 2020 to acquire in
vivo MR images, showcasing the practical applications of their
pioneering research \cite{OReilly2021-ep}. In 2023, de Vos, Remis
and Webb published a summary of the design of an oint-of-care halbach
array low-field \gls{mri} system \cite{De_Vos2023-pb}.

@@

\textbf{Magnet Characerisation}

The shimming process described describes how, after the field magnet has
been set up, if the homogeneous magnetic flux densities are not
sufficient, these can be adjusted manually by means of adjustments to
the setup or, if the hardware allows it, by software. In addition, the
causes that cause the inhomogeneity, the output permanent magnet, are
also known. As a result, there is the possibility of using the shimming
process or checking the permanent magnets used in advance before they
are used in a Hallbach configuration.

@@

Before naming the research focus, it is important to understand the
difference and connection between deviation and resulution of the
system. To measure a deviation of better than \emph{1000}\gls{ppm} in a
\emph{50mT} magnetic field, a resolution that is less than
\emph{1000}\gls{ppm} of \emph{50mT} is needed.

@@

It is essential to emphasize that the intention is not to characterize
the magnets; the sensores which might be used for characterisation are
be analised and evaluated.

@@

The purpose of the framework is to enable the automated acquisition of
measurement data from various connected hadware sensors. The user should
be able to configure various measurement series, which should then be
carried out by the framework without further user interaction.

@@

This makes it easy to integrate an own measuring devices into the
\gls{mrp} ecosystem at a later date. This is only possible with a
minimal functional hardware and firmware setup and was developed for
this purpose first.

@@

A key aspect of this selection was the preference for sensors with
digital interfaces to facilitate implementation in the circuit layout
since these kind of sensors are easy to integrate compared to
non-digital sensors, which require specific frameworks. The integration
of integrated temperature sensors represents a significant enhancement
that will later enable precise temperature compensation.

The use of analog sensors was purposefully avoided, though they are
suitable for more precise measurements and extended measuring ranges.
They were excluded because they require more carefully designed circuits
and more complicated energy management.

@@

All parts are produced using the 3D printing additive manufacturing
processes. The sensor circuit board was glued underneath the magnet
holder. This is interchangeable, so different distances between sensor
and magnet can be realised.

@@

All the necessary components and their circuitry are recorded on a
\gls{pcb} \ref{1D_sensor_schematic_and_circuit_board.png} and
subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts ontop of
the sensor \gls{ic}s.

Special attention was paid to the provision of an accessible
SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
synchronization and also offers options for later extensions. This
functionality opens up the possibility of synchronising data from
different sensors to achieve precise and coherent measurement results.
Overall, this integrated approach represents an effective solution for
the flexible evaluation of sensors and helps to optimise the development
process.

@@

An important component is that as many common sensors as possible can be
easily connected without having to adapt the firmware. This modularity
was implemented using abstract class design. These are initiated
according to the sensors found at startup. If new hardware is to be
integrated, only the required functions \ref{lst:CustomSensorClass} need
to be implemented.

@@

After execution of the setup routine is completed, the system switches
to an infinite loop, which processes several possible actions. One task
is, to react to user commands which can be sent to the system by the
user via the integrated \gls{cli}. All sensors are read out via a timer
interval set in the setup procedure and their values are stored in a
ringbuffer. Ring buffer offers efficient data management in limited
memory. Its cyclic structure enables continuous overwriting of older
data, saves memory space and facilitates seamless processing of
real-time data.

@@

Each sensor that is loaded with the firmware, registeres on to the host
\gls{pc} as a serial interface. There are several ways for the user to
interact with the sensor:

\begin{itemize}
\tightlist
\item
  Use with \gls{mrp} \ref{software-readout-framework}-libaray
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{debian bookworm x64},
\item
  \gls{mrp} \ref{software-readout-framework}-library - Version
  \emph{1.4.1}
\item
  Unified Sensor \ref{unified-sensor}-firmware - Version \emph{1.0.1}
\end{itemize}

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an intial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to \emph{secondary} mode
and synchronise the measurements based on each sync pulse received.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The synchronisation status can be queried via the user interface
\ref{communication-interface} using the \emph{opmode}
\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
implementation here was that there is no numbering or sequence of the
individual sensors.

@@

\hypertarget{d-fullsphere}{%
\subsection{3D: Fullsphere}\label{d-fullsphere}}

@@

The 3D fullsphere sensor
\ref{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
offers the possibility to create a 3D map of the inserted magnet.

The graphic
\ref{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which was detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder.

@@

As the magnets in the motors, as with the screws used in the 1D sensor,
can influence the measurements of the magnetic field sensor, the
distance between these components and the sensor or magnets was
increased. The turntable and its drive motor are connected to each other
via a belt.

On the electrical side, it also consists of a \emph{SKR-Pico} stepper
motor controller, together with the \emph{TLV493D} magnetic field
sensor. This was chosen because of its larger measuring range and can
therefore be used more universally without having to change the sensor
of the arm.

@@

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware is adapted using a separate
build configuration. In order to be able to read and correctly interpret
the data from the microcontoller, the serial protocol of the sensor is
implemented in a customised version of the \emph{CustomSensor} class
\ref{lst:CustomSensorClass}.

@@

\begin{itemize}
\tightlist
\item
  Data acquisition - from hardware sensors \ref{unified-sensor} or other
  data sources
\item
  Storage - export of data in various open formats
  \ref{storage-and-datamanagement}
\item
  Analysis - algorithms to analyze different data sets \ref{analysis}
\end{itemize}

@@

This also fulfills the goal of making individual user-created algorithms
interchangeable. If the user now wishes to use a different \gls{cad}
algorithm instead of the \emph{HalbachMRIDesigner}
\cite{HalbachMRIDesigner}, the other steps can simply be preserved
and only the new step needs to be implemented.

@@

To configure parameters, ensuring a tailored approach to the entire
measurement process, these parameters act as a cessential bridge between
user preferences and the robust capabilities of the \emph{MRPReading}
module.

@@

The following code snippet \ref{lst:json_export_format_example} shows
the \gls{json} structure which is generated when a measurement thatt
using the library is exported. It can be seen that by using the
\gls{json} format, all measurement points and metadata are available in
readable plain text.

@@

The extention modules build on the core modules and offer the user
additional basic functionalities. These include functions for data
acquisition, visualisation and analysis.

@@

\begin{itemize}
\tightlist
\item
  \emph{std\_deviation} - Standard deviation
\item
  \emph{mean} - Mean value
\item
  \emph{variance} - Variance
\item
  \emph{CoG} - Center of gravity
\item
  \emph{binning} - Distribution of a sample by means of a histogram
\item
  \emph{k-nearest} - K-nearest neighbors
\end{itemize}

@@

Multibe sensor can be connected to any \gls{pc} which is available on
the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
footprint and low power consumption make it a good choice. It can also
be used in a temperature chamber.

@@

The figure
\ref{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png} shows
the modified \emph{multi-proxy - multi-sensor} topology. Here, both
proxy instances do not communicate directly with the \emph{control}
\gls{pc}, but the proxy instance \emph{remote} \gls{pc} \emph{\#2} can
acces the proxy running on \emph{remote} \gls{pc} \emph{\#1}.

@@

This final example shows the use of the \emph{MRPVisualisation} module,
which provides general functions for visualising measurements. The
visualisation optionsmakes it possible to visually assess the results of
a measurement. This is particularly helpful for full-sphere measurements
recorded with the \emph{3D: Fullsphere} \ref{d-fullsphere} sensor. The
sub-module \emph{MRPPolarVisualisation} is specially designed for these.
The figure
\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
shows a plot of a fullsphere measurement. It is also possible to export
the data from the \emph{MRPAnalysis} module graphically as diagrams. The
\emph{MRPVisualisation} modules are used here. The following example
\ref{lst:mrpexample_visualisation} shows the usage of both modules.

@@

After the measurements have been generated, they are provided with a
position and rotation offset according to the Halbach design and
calucation scheme \cite{HallbachMagnetDesignPaper} using the
\emph{MRPHalbachArrayGenerator} module.

@@

Although such examples are provided in the documentation, it must be
possible for programming beginners in particular to use them. To
simplify these tasks, a \gls{cli}
\ref{Example_measurement_analysis_pipeline.png} is implemented. The
libaray \gls{cli} implements the following functionalities:

@@

One important point that improves usability for users is the simple
installation of all \gls{mrp} modules. As it is created in the Python
programming language, there are several public package registry where
users can provide their software modules. Here, \emph{PyPi}
\cite{PyPI}
\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}
\cite{MagneticReadoutProcessingPyPI} is the most commonly used
package registry and offers direct support for the package installation
programm \gls{pip} \ref{lst:setup_lib_with_pip}.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Hardware preperation}: Users can prepare measurements using
  the implemented framework. This includes the placement of the sensors
  and the selection of the relevant parameters for the characterisation
  of the permanent magnets.
\item
  \textbf{Configuration of the measurement}: The software provides a
  user-friendly interface for configuring the measurement parameters.
  Users can make the desired settings here and customise the framework
  to their specific requirements.
\item
  \textbf{Custom algorithm implementation}: An important contribution of
  the \gls{mrp} ecosystem is the possibility for users to implement
  their own algorithm for data analysis. This allows customisation to
  specific research questions or experimental requirements.
\item
  \textbf{Execution of analysis pipeline}: The analysis pipeline can
  then be executed with the implemented algorithm. The collected
  measurement data is automatically processed and analysed to extract
  characteristic parameters of the permanent magnets.
\end{enumerate}

@@

\hypertarget{hardware-preperation}{%
\section{Hardware preperation}\label{hardware-preperation}}

@@

For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor is
used for the evaulation of the framework. As this is equipped with an
exchangeable magnetic holder mount, suitable holders are required for
the magnets to be measured. Ten random \emph{N45 12x12x12mm} neodymium
magnets were used, which are shown in figure
\ref{Ten_numbered_test_magnets_in_separate_holders.png}.

@@

The parameter *\_readings* should later receive the imported
measurements from the \emph{stage rawimport}
\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
\emph{IP\_return\_count} parameter specifies the number of best
measurements that are returned. The return parameter is a list of
measurements containing the most similar measurements, measured by the
smallest distance between all measurements. The distance for each
measurement is determined using the center of gravity function
\emph{CoG}, the length is then calculated from the result vector. This
value can then be used for sorting.

@@

On the right-hand side
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
the measured values are plotted as a result of the filter algorithm. As
the \emph{IP\_return\_count} parameter was set to four, only the four
most similar measurements were exported here. It can be seen from the
plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value is
calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (magnet type, dimensions, sensor distance) as
they correspond to the mechanical structure of the used hardware sensor
\ref{d-fullsphere}.

@@

The filter algorithm implemented by the user is thus successfully
executed using the user-programmable pipeline. The calculation result
waiss successfully verified using raw measurement data and the final
result of the algorithm.

@@

In addition, the basic application by the user is demonstrated using an
example. This makes it possible to systematically characterise magnets
from the software and readout hardware side by means of data
acquisition, storage and analysis.

@@

\begin{itemize}
\tightlist
\item
  Measure a wide range of different permanent magnets with regard to
  their systematic field strength
\item
  Automated measurement of the homogeneity of Hallbach rings with an
  accuracy of less than \emph{1000\gls{ppm}}
\end{itemize}

@@

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were used for sensor characterisation. The additional column for the
\emph{Background-Noise} is taken from the respective data sheets of the
sesors and will be verified in the later \emph{Background-Noise}
measurement \ref{sensor-characterisation-background-noise}.

@@

In the raw data plot, as well as its mean value \(\mu_{rv}\) of both
sensors, an offset can also be recognised, which is dependent on the
ambient conditions. For verification, a reference measurement of the
environment was carried out with the calibrated \emph{Voltcraft GM70}
Telsameter next to the sensor \gls{ic} This provides a \emph{real}
baseline value of \(\mu_{rev}\)=-21\(\mu\)T.

>>>>

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field \gls{mri} research and
applications, articulates the research question driving this thesis and
delineates the anticipated usecases and benefits that will be explored
and analysed throughout the study.

@@

In response to this, there is a growing interest in developing low-field
\gls{mri} systems that utilize in many cases permanent magnets. These
systems, while offering advantages in energy efficiency and reduced
complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While typically calculated images have lower resolution due to
lower magnetic field strength, low-field systems facilitate the
comparison of different field behaviours and the identification of all
kinds of irritations. O'Reilly and Teeuwisse and de Gans
\cite{OReilly2019-rn} have already demonstrated low-cost and
small-scale implementations with low-field \gls{mri} in 2021 calculating
images of a head successfully.

@@

Completed \gls{mri} systems pose significant challenges for
retrospective adjustments, particularly when individual magnets impact
the overall homogeneity of the magnetic field. While deviations in
homogeneity can be measured post-assembly, the intricate task of
readjustment is taken into account. It is less cost-intensive and less
complicated to measure the magnets proactively, prior to the
finalization of the \gls{mri} system.

@@

For modern medical imaging high-field superconducting magnets dominate
most \gls{mri} machines, providing high black-withe image resolution.
However, the substantial costs, space requirements and safety
considerations cause considerable challenges.

\gls{mri} relies on the presence of a robust magnetic field, and over
time, there has been a continual push to enhance the strength of these
magnetic fields. This strength is quantified in units of Tesla {[}T{]},
commonly referred to as the \emph{B0} field in medical contexts, while
physicists use the term magnetic field induction. The \gls{snr} is
proportional to the magnetic \emph{B0} field; growing magnetic field
leads automatically to higher \gls{snr}. The initial \emph{B0} field of
an \gls{mri} aims to be homogeneous, for image acquisition the second
step requires inhomogeneity of the \emph{B0} field to stimulate spin in
the atoms of materials. For high resolution images, the initial
\emph{B0} field aims to be a homogeneous as possible.

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The graphic
\ref{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring, in which in this case eight
cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
magnetic flux densities of around \emph{20mT}.

@@

The Halbach magnetic array appears as a essential element for future
Magnet characterisation. Based on this fact this thesis centres on
assessing the sensors' applicability, the Halbach magnetic array serves
as a tool for later measurements, although its implementation and
further discussion will not be the primary focus.

@@

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
\cite{OReilly2019-rn} in 2019.This innovative setup is subsequently
employed in 2020 to acquire in vivo MR images, showcasing the practical
applications of their pioneering research \cite{OReilly2021-ep}. In
2023, de Vos, Remis and Webb published a summary of the design of a
point-of-care Halbach array low-field \gls{mri} system
\cite{De_Vos2023-pb}.

Within the research domain, various implementations came up. An exemplar
instance is the work by O'Reilly, Teeuwisse, and Webb, who introduced a
groundbreaking ``three-dimensional \gls{mri} in a homogeneous 27cm
diameter Bore Halbach Array magnet'' \cite{OReilly2019-rn} in 2019.
This innovative setup is subsequently employed in 2020 to acquire in
vivo MR images, showcasing the practical applications of their
pioneering research \cite{OReilly2021-ep}. In 2023, de Vos, Remis
and Webb published a summary of the design of an oint-of-care halbach
array low-field \gls{mri} system \cite{De_Vos2023-pb}.

@@

\textbf{Magnet Characterisation}

The shimming process described describes how, after the field magnet has
been set up, if the homogeneous magnetic flux densities are not
sufficient, these can be adjusted manually by means of adjustments to
the setup or, if the hardware allows it, by software. In addition, the
causes that cause the inhomogeneity, the output permanent magnet, are
also known. As a result, there is the possibility of using the shimming
process or checking the permanent magnets used in advance before they
are used in a Halbach configuration.

@@

Before naming the research focus, it is important to understand the
difference and connection between deviation and resolution of the
system. To measure a deviation of better than \emph{1000}\gls{ppm} in a
\emph{50mT} magnetic field, a resolution that is less than
\emph{1000}\gls{ppm} of \emph{50mT} is needed.

@@

It is essential to emphasize that the intention is not to characterize
the magnets; the sensors which might be used for characterisation are be
analysed and evaluated.

@@

The purpose of the framework is to enable the automated acquisition of
measurement data from various connected hardware sensors. The user
should be able to configure various measurement series, which should
then be carried out by the framework without further user interaction.

@@

This makes it easy to integrate an own measuring devices into the
\gls{mrp} ecosystem at a later date. This is only possible with a
minimal functional hardware and firmware setup and is developed for this
purpose first.

@@

A key aspect of this selection is the preference for sensors with
digital interfaces to facilitate implementation in the circuit layout
since these kind of sensors are easy to integrate compared to
non-digital sensors, which require specific frameworks. The integration
of integrated temperature sensors represents a significant enhancement
that will later enable precise temperature compensation.

The use of analog sensors is purposefully avoided, though they are
suitable for more precise measurements and extended measuring ranges.
They were excluded because they require more carefully designed circuits
and more complicated energy management.

@@

All parts are produced using the 3D printing additive manufacturing
processes. The sensor circuit board is glued underneath the magnet
holder. This is interchangeable, so different distances between sensor
and magnet can be realised.

@@

All the necessary components and their circuitry are recorded on a
\gls{pcb} \ref{1D_sensor_schematic_and_circuit_board.png} and
subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts on top of
the sensor \gls{ic}s.

Special attention is paid to the provision of an accessible
SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
synchronization and also offers options for later extensions. This
functionality opens up the possibility of synchronising data from
different sensors to achieve precise and coherent measurement results.
Overall, this integrated approach represents an effective solution for
the flexible evaluation of sensors and helps to optimise the development
process.

@@

An important component is that as many common sensors as possible can be
easily connected without having to adapt the firmware. This modularity
is implemented using abstract class design. These are initiated
according to the sensors found at startup. If new hardware is to be
integrated, only the required functions \ref{lst:CustomSensorClass} need
to be implemented.

@@

After execution of the setup routine is completed, the system switches
to an infinite loop, which processes several possible actions. One task
is, to react to user commands which can be sent to the system by the
user via the integrated \gls{cli}. All sensors are read out via a timer
interval set in the setup procedure and their values are stored in a
ring buffer. Ring buffer offers efficient data management in limited
memory. Its cyclic structure enables continuous overwriting of older
data, saves memory space and facilitates seamless processing of
real-time data.

@@

Each sensor that is loaded with the firmware, registers on to the host
\gls{pc} as a serial interface. There are several ways for the user to
interact with the sensor:

\begin{itemize}
\tightlist
\item
  Use with \gls{mrp} \ref{software-readout-framework}-library
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{Debian bookworm x64},
\item
  \gls{mrp} \ref{software-readout-framework}-library - Version
  \emph{1.4.1}
\item
  Unified Sensor \ref{unified-sensor}-firmware - Version \emph{1.0.1}
\end{itemize}

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an initial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to \emph{secondary} mode
and synchronise the measurements based on each sync pulse received.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The synchronisation status can be queried via the user interface
\ref{communication-interface} using the \emph{opmode}
\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
implementation here is that there is no numbering or sequence of the
individual sensors.

@@

\hypertarget{d-full-sphere}{%
\subsection{3D: Full Sphere}\label{d-full-sphere}}

@@

The 3D full sphere sensor
\ref{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
offers the possibility to create a 3D map of the inserted magnet.

The graphic
\ref{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which is detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder.

@@

As the magnets in the motors, as with the screws used in the 1D sensor,
can influence the measurements of the magnetic field sensor, the
distance between these components and the sensor or magnets is
increased. The turntable and its drive motor are connected to each other
via a belt.

On the electrical side, consists of a \emph{SKR-Pico} stepper motor
controller on the one hand side and a \emph{TLV493D} magnetic field
sensor on the other hand side. This is chosen because of its larger
measuring range and can therefore be used more universally without
having to change the sensor of the arm.

@@

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware is adapted using a separate
build configuration. In order to be able to read and correctly interpret
the data from the microcontroller, the serial protocol of the sensor is
implemented in a customised version of the \emph{CustomSensor} class
\ref{lst:CustomSensorClass}.

@@

\begin{itemize}
\tightlist
\item
  Data acquisition - from hardware sensors \ref{unified-sensor} or other
  data sources
\item
  Storage - export of data in various open formats
  \ref{storage-and-datamanagement}
\item
  Analysis - algorithms to analyse different data sets \ref{analysis}
\end{itemize}

@@

This also fulfils the goal of making individual user-created algorithms
interchangeable. If the user now wishes to use a different \gls{cad}
algorithm instead of the \emph{HalbachMRIDesigner}
\cite{HalbachMRIDesigner}, the other steps can simply be preserved
and only the new step needs to be implemented.

@@

To configure parameters, ensuring a tailored approach to the entire
measurement process, these parameters act as a essential bridge between
user preferences and the robust capabilities of the \emph{MRPReading}
module.

@@

The following code snippet \ref{lst:json_export_format_example} shows
the \gls{json} structure which is generated when a measurement that
using the library is exported. It can be seen that by using the
\gls{json} format, all measurement points and metadata are available in
readable plain text.

@@

The extension modules build on the core modules and offer the user
additional basic functionalities. These include functions for data
acquisition, visualisation and analysis.

@@

\begin{itemize}
\tightlist
\item
  \emph{std\_deviation} - Standard deviation
\item
  \emph{mean} - Mean value
\item
  \emph{variance} - Variance
\item
  \emph{CoG} - Centre of gravity
\item
  \emph{binning} - Distribution of a sample by means of a histogram
\item
  \emph{k-nearest} - K-nearest neighbours
\end{itemize}

@@

Multiple sensor can be connected to any \gls{pc} which is available on
the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
footprint and low power consumption make it a good choice. It can also
be used in a temperature chamber.

@@

The figure
\ref{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png} shows
the modified \emph{multi-proxy - multi-sensor} topology. Here, both
proxy instances do not communicate directly with the \emph{control}
\gls{pc}, but the proxy instance \emph{remote} \gls{pc} \emph{\#2} can
access the proxy running on \emph{remote} \gls{pc} \emph{\#1}.

@@

This final example shows the use of the \emph{MRPVisualisation} module,
which provides general functions for visualising measurements. The
visualisation options make it possible to visually assess the results of
a measurement. This is particularly helpful for full-sphere measurements
recorded with the \emph{3D: Fullsphere} \ref{d-fullsphere} sensor. The
sub-module \emph{MRPPolarVisualisation} is specially designed for these.
The figure
\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
shows a plot of a fullsphere measurement. It is also possible to export
the data from the \emph{MRPAnalysis} module graphically as diagrams. The
\emph{MRPVisualisation} modules are used here. The following example
\ref{lst:mrpexample_visualisation} shows the usage of both modules.

@@

After the measurements have been generated, they are provided with a
position and rotation offset according to the Halbach design and
calculation scheme \cite{HallbachMagnetDesignPaper} using the
\emph{MRPHalbachArrayGenerator} module.

@@

Although such examples are provided in the documentation, it must be
possible for programming beginners in particular to use them. To
simplify these tasks, a \gls{cli}
\ref{Example_measurement_analysis_pipeline.png} is implemented. The
library \gls{cli} implements the following functionalities:

@@

One important point that improves usability for users is the simple
installation of all \gls{mrp} modules. As it is created in the Python
programming language, there are several public package registry where
users can provide their software modules. Here, \emph{PyPi}
\cite{PyPI}
\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}
\cite{MagneticReadoutProcessingPyPI} is the most commonly used
package registry and offers direct support for the package installation
program \gls{pip} \ref{lst:setup_lib_with_pip}.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Hardware preparation}: Users can prepare measurements using
  the implemented framework. This includes the placement of the sensors
  and the selection of the relevant parameters for the characterisation
  of the permanent magnets.
\item
  \textbf{Configuration of the measurement}: The software provides a
  user-friendly interface for configuring the measurement parameters.
  Users can make the desired settings here and customise the framework
  to their specific requirements.
\item
  \textbf{Custom algorithm implementation}: An important contribution of
  the \gls{mrp} ecosystem is the possibility for users to implement
  their own algorithm for data analysis. This allows customisation to
  specific research questions or experimental requirements.
\item
  \textbf{Execution of analysis pipeline}: The analysis pipeline can
  then be executed with the implemented algorithm. The collected
  measurement data is automatically processed and analysed to extract
  characteristic parameters of the permanent magnets.
\end{enumerate}

@@

\hypertarget{hardware-preparation}{%
\section{Hardware preparation}\label{hardware-preparation}}

@@

For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor is
used for the evaluation of the framework. As this is equipped with an
exchangeable magnetic holder mount, suitable holders are required for
the magnets to be measured. Ten random \emph{N45 12x12x12mm} neodymium
magnets were used, which are shown in figure
\ref{Ten_numbered_test_magnets_in_separate_holders.png}.

@@

The parameter *\_readings* should later receive the imported
measurements from the \emph{stage rawimport}
\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
\emph{IP\_return\_count} parameter specifies the number of best
measurements that are returned. The return parameter is a list of
measurements containing the most similar measurements, measured by the
smallest distance between all measurements. The distance for each
measurement is determined using the centre of gravity function
\emph{CoG}, the length is then calculated from the result vector. This
value can then be used for sorting.

@@

On the right-hand side
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
the measured values are plotted as a result of the filter algorithm. As
the \emph{IP\_return\_count} parameter is set to four, only the four
most similar measurements were exported here. It can be seen from the
plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value is
calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (magnet type, dimensions, sensor distance) as
they correspond to the mechanical structure of the used hardware sensor
\ref{d-fullsphere}.

@@

The filter algorithm implemented by the user is thus successfully
executed using the user-programmable pipeline. The calculation result is
successfully verified using raw measurement data and the final result of
the algorithm.

@@

In addition, the basic application by the user is demonstrated based on
an example. In this way is possible to systematically characterise
magnets from the software and readout hardware side by means of data
acquisition, storage and analysis.

@@

\begin{itemize}
\tightlist
\item
  Measure a wide range of different permanent magnets with regard to
  their systematic field strength
\item
  Automated measurement of the homogeneity of Halbach rings with an
  accuracy of less than \emph{1000\gls{ppm}}
\end{itemize}

@@

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were used for sensor characterisation. The additional column for the
\emph{Background-Noise} is taken from the respective data sheets of the
sensors and will be verified in the later \emph{Background-Noise}
measurement \ref{sensor-characterisation-background-noise}.

@@

In the raw data plot, as well as its mean value \(\mu_{rv}\) of both
sensors, an offset can also be recognised, which is dependent on the
ambient conditions. For verification, a reference measurement of the
environment is carried out with the calibrated \emph{Voltcraft GM70}
Telsameter next to the sensor \gls{ic} This provides a \emph{real}
baseline value of \(\mu_{rev}\)=-21\(\mu\)T.
